---
title: "India Hurricanes DiD 2"
author: "Danielle Handel"
date: "11/27/2020"
---

# This code combines the cleaned hurricane data and DHS neonatal mortality data and runs a FE regression of individual neonatal death on treatement by a hurricane. 


```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "C:/Users/asyah/Desktop/Fall 2020/Thesis/Disaster/", echo = TRUE, tidy.opts=list(width.cutoff=60),tidy=TRUE)


library(dplyr)
library(lfe)
library(broom)
library(reactable)
library(zoo)
library(stargazer)
```

## Reading in the hurricane data

* district boundaries directly from DHS
* paths from NOAA; only includes those technically considered hurricanes

```{r}

hur_dat <- read.csv("India disaster data/india map/hurricane_data_final_9mos.csv") 

# count a district as treated for a birth month if it is more than 50% covered by hurricanes in the 9 month period prior
hur_dat$treated <- ifelse(hur_dat$coverage >= .5, 1, 0)

# what the hurricane data looks like
hur_dat %>% reactable()

```

## DHS neonatal mortality data  

```{r}
dhs_dat <- read.csv("Neonatal and infant mortality data/dhs_2015_data_v5.csv")


dhs_dat <- dhs_dat %>% dplyr::rename(district_code = GEOALT_IA2015, year = KIDBIRTHYR, date = birthday_full) %>% filter(RESIDENT == 1) %>% mutate(date = as.Date(as.yearmon(date)))

# what the DHS data looks like

dhs_dat %>% reactable()
```

## Merging the data to indicate treated/not treated for each birth 
```{r}
# merge hurricane and births data by district/year
# get rid of births with missing education level for mother

merged_dat <- merge(hur_dat, dhs_dat, by = c("district_code","date"), all.y = TRUE) %>% filter(EDUCLVL != 8)

# load in a list of the regions in the hurricane zone

disaster_region <- read.csv("India disaster data/india map/hurricane_region_districts.csv")

# drop all districts not in the hurricane zone 

merged_dat <- merged_dat %>% filter(district_code %in% disaster_region$x)

# since hurricane data only includes treated districts, assign a zero for treatment to any districts without a treatment value after merging 

merged_dat$treated <- ifelse(is.na(merged_dat$treated), 0, merged_dat$treated)

# select relevant variables 

merged_dat2 <- merged_dat %>% dplyr::select("date","treated","IDHSPID","PERWEIGHT","year","URBAN","MARSTAT","WEALTHS","CHEB","neo_death","RELIGION","KIDSEX","KIDBORD","EDUCLVL","district_code","KIDTWIN")%>%
    mutate(across(c("URBAN","MARSTAT","RELIGION","KIDSEX","KIDBORD","EDUCLVL","KIDTWIN"), as.factor))
```

## Looking at births/ neonatal deaths per year

```{r}
# number of births/ deaths by year 

year_sum <- merged_dat2 %>% group_by(date) %>% summarize(neo_deaths = sum(neo_death), total_births = n())

# create a list of the years with more than 800 births in the sample 

many_births <- year_sum %>% filter(total_births >= 800)

# peak at year_sum 

year_sum %>% reactable()

# remove years with two few births 

few_merged_dat2 <- merged_dat2 %>% filter(date %in% many_births$date)

```



## FE with SEs clustered at the district level

* individual-level controls: 
    + education level (mother)
    + religion
    + mother's marital status
    + child gender
    + birth order
    + twin or single birth
    + rural or urban
* district-level controls: 
    + average education level
    + average income 
    + percentage urban/rural
* FEs
    + district
    + month
    + state by year

$$neonatalDeath_{idc} = \beta_0 + \beta_1 treated_{dc} + \alpha_{d} + \alpha_c + \alpha_{sy} + X_{i} + Z_{d} + u $$

```{r}
# create a dummy for education level
# select relevant variables

district_controls <- read.csv("w_district_controls.csv")


reg_data2 <- merge(few_merged_dat2, district_controls, by.x = "district_code", by.y = "GEOALT_IA2015", all.x = T)

# load in state codes 

state_key <- read.csv('Neonatal and infant mortality data/state_key.csv')

# add in state codes

reg_data3 <- merge(reg_data2, state_key, by = "district_code", all.x = T)

# remove date format 

reg_data3$date <- as.character(reg_data3$date)

```

## Completed data set used for regression

```{r}
reg_data3 %>% reactable()
```

## Regression

I cannot figure out why, but the district-level regressors all return NA coefficients. 

```{r}
reg1 <- felm(neo_death ~ treated + EDUCLVL + URBAN + MARSTAT + KIDSEX + KIDTWIN + KIDBORD + RELIGION + avg_wealth + average_ed + urban_per| district_code + date + factor(state_code):factor(year)|0|district_code, data = reg_data3, 
     weights = reg_data3$PERWEIGHT)

stargazer(reg1)
```




